A methodology for calculating active force-time functions from broadband piezoelectric sensors

### 2020-05-01 Article_file_Source_reconstruction.tex
Updates from Overleaf

\begin{abstract}
We preform active source tests using a piezoelectric (PZT) actuator that was excited by a rapid transient high voltage pulse (HVP). The crystal geometry of the actuator was a conical frustum where the tip was placed centrally on top of a thick steel plate. We studied the elastodynamic stress waves  (between 100 kHz to 1 MHz) produced by the source, whereby the HVP pulse was converted to a rapid transient force-time function ($f_{j}$) via the piezoelectric effect.  The source produced mechanical vibrations ($u_{k}$) throughout the sample and was measured ($s$) using an array of 13 passive conical PZT receivers, at known locations on the bottom of the steel plate. Dynamic Green's functions ($G_{kj}$) were calculated using generalized ray theory and the known instrument responses ($I_{k}$) were pre-calculated from a series of ball drop experiments for all source-receiver pairs. Using these parameters, we were able to reconstruct the force-time function of the PZT actuator. As predicted from the literature, the actuator behaved as an under-damped oscillator with a peak loads, decay rate and undamped resonant frequency of $A_{0}$ = 3.3 $\pm$ 0.8 N, $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, respectively.  Both the decay rate and resonant frequency were determined as by minimizing the error between theoretical displacements for this force-time function over all 13 receiver measurements. Understanding calibrated force-time functions from PZT actuators can help to develop time-dependent and nondestructive characterization of many acoustic emission system components, such as the receiving transducers or the transfer media itself, in non-accessible laboratory environments. 
\end{abstract}

@@

Understanding the theory associated with elastodynamic wave propagation in materials has proven to be highly applicable to many disciplines in science and engineering. The general principle follows that by measuring the kinematic motion at a point in/on the media, perturbed by the incoming elastic waves, we can use wave propagation theory to back calculate critical information. The particle motions within the body are governed by the wave equation and the body itself can be solid or fluid materials and the waves carry both information of the media in which they propagate and of the source which caused them. This concept has made for many practical and highly interdisciplinary application. It has been widely applied in the fields of seismology, biomedicine, and nondestructive testing, to name a few.

The concept relies heavily on understanding attributes to three key components: (\textit{i}) source, (\textit{ii}) material and (\textit{iii}) receiver. In most applications, these waves are non-intrusive, propagating elastically through the medium from the source to receiver. From this, the problem benefits from \textit{source-receiver reciprocity} and due to symmetry of the wave equation, \textit{time invariance} applies, making this a versatile and flexible tool.

Sources can occur due to anthropogenic forcing, for example, rock samples subjected to outside stresses in a laboratory setting can crack locally, generating acoustic emissions \citep[e.g.][]{Lei2014}. These emission cause vibrations within sample using peizoelectric sensors in the laboratory. This phenomena also scales up to mining activities where microseismic studies are performed to ensure safety during engineering activities \citep[e.g.][]{Manthei2018}. Further up the scale, that large earthquakes occurring on faults in nature, occur naturally, activated by slow tectonic loading on geologic timescale. At each scale, the physic governing wave propagation holds and the vibrations through the medium are studied with arrays of sensors that are sensitive to vibrations at a range of frequencies. When the sources occur due to spontaneous instability, we consider this to be passive monitoring.

Sources can also be actively imposed, meaning that a transient force must manufactured within or on the body of interest. Since the wave equation still governs the resulting motions throughout the body, it becomes an important tool to study the material properties or changes them over time. Moreover, if multiple sources can be manufactured, understanding structures becomes possible through, for example, tomographic inversion.  This has been particularly important in the medical industry, where ultrasonic sensors can act as source or receivers and structures within the body can non-invasively be reconstructed through ultrasound computer tomography (USCT) \citep[e.g.][]Christensen1988}. While this methods assume that acoustic waves propagate (i.e. fluid), \textit{active field survey} in geophysics assume that the material is a solid and can reconstruct the subsurface to a high degree of certainty using `shot gather' approach and having well-constrained and repeatable sources.

@@

The study of spherical waves in an elastic half-space was solved by \citet{Lamb1904} who was interested in the kinematic motions on a surface using the integral of plane waves solutions from \citet{Rayleigh1885}. More specifically, the Lamb's problem focuses on determining the elastic disturbance resulting from a point force in/on a half space. These early studies aimed at understanding phase arrivals and their relationship to earthquake sources in the field of seismology. These seminal investigations have been followed by many hundreds of studies that have use different mathematical approaches to solve the wave equation \citep[e.g. ch 6 in][]{Aki2002}.These studies vary in complexity in the media (in-homogeneous layered, or anisotropic, etc.), to complex source features (double couple, compensated-linear-vector-dipole, etc.) and use a range of different methods to solve (theoretical closed-form solutions, numerical methods, etc.). We adopt the approach presented by \citet{Johnson1974} that derived the complete solution to the three-dimensional Lamb’s problem derived using the Cagniard--de Hoop method. This solution is used to study the mechanical disturbances from sources in an elastic half-space and has been to a numerical generalized ray theory code by \citet{Hsu1985} \citep[see also][]{McLaskey2011, McLaskey2012, Selvadurai2019}.

While more complex sources have been considered to model earthquakes, such as the single and double couple source, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a). In Figure \ref{fig2}(a), we show the cross-section A-A from Figure \ref{fig1}(b). The source is produced by pulsing the piezoelectric actuator on the top surface using the experimental facilities described in Figure \ref{fig1}. The impulsive actuation of the PZT crystal on the steel plate produces a rapid transient source causing elastodynamic stress waves to propagate outwards. In Figure \ref{fig2}, the coloured region represents a synthetic representation of the velocity wave-field and is only provided as a reference and is not representative of the source produced from the PZT actuator (which is to be determined later). For this example, a snapshot of the velocity wave-field, produced from a capillary fracture is shown from numerical finite element simulations in ABAQUS \citep[adapted from fig. 2][]{Selvadurai2019}.

Properties of the source creating the stress waves is important. \citet{Breckenridge1990} states that the ideal source is infinitesimal in size, has a force-time function of a step or delta function, and generates large amplitudes. He performed important study of a variety of sources including pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive, noting that each type is imperfect and has its trade offs. In this study, we look to aim to understand the PZT actuator (similar to conical transducer) which we can leverage to non-invasively study the \textit{in situ} absolute calibration conditions inside a less accessible experimental facility (e.g. triaxial pressure cell). To model the force-time function produced conical sensor, we first simplify the sequence of events and their components that link the source to the recorded signal.

In Figure \ref{fig2}(a), we show the five components of ``toolchain'' that is used to link the source to the measured signal. The PZT actuator is used to produce a (\textit{1}) \textbf{rapid transient force} $f_{j}$ on the top surface at a point $\mathbf{\xi}$ of the steel platen at a delayed time $\tau$. Elastic stress waves propagate through the plate and the theoretical elastic displacement field throughout the body can be computed using the (\textit{2}) \textbf{Green's function} $G_{kj}$. The Green's functions map the (\textit{3}) \textbf{mechanical vibrations} $u_{k}$ at $\mathbf{x}$ and time $t$ from the force at $\mathbf{\xi}$ and time $\tau$. A passive sensor, on the bottom surface at point $\mathbf{x}$ and attempts to measure the theoretical displacements $u_{k}$. Unfortunately, the passive sensors always will distort the (\textit{4}) \textbf{measured signal}  $s$ according to its (\textit{5}) \textbf{instrument response} $i_{k}$ at position $\mathbf{x}$ and time $t$.

\begin{figure}[h]
     	\centering
\includegraphics[scale= 1.0]{FIG2.pdf} 
\caption{Fundamental features related to the Lamb problem that relates elastodynamic displacements in an elastic half-space to a source (force-time) function. The velocity displacement field is shown for reference only and was adopted from \citet{Selvadurai2019}. P and S waves are highlighted for reference only. The PZT actuator is located centrally on the top of the steel plate and passive (recording) sensors are shown below for the Section A-A from Figure \ref{fig1}(b).}
	\label{fig2} 
\end{figure}
\section{Experimental facilities}
\subsection{General}

We study elastodynamic waves propagating through an elastic isotropic, homogeneous steel plate. Using an electro-mechanical piezocomposite actuator, deliver impulsive sources on to the top surface of the steel specimen. On the bottom, an array of 13 piezoelectric (lead zirconate titanate, PZT) transducers are mounted in an aluminium array holder. The aim of this study is to better understand the force produced by the piezoelectric actuator by studying the waves produced at different locations on the bottom of the specimen.

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1.0]{FIG1.pdf} 
\caption{\textbf{(a)} General schematic of the calibration station located in the Rock Physics and Mechanics Laboratory at ETH Zurich. We used apparatus to apply an active source downwards, which was centrally located on the top of a steel platen. This produced elastodynamic stress waves that are measured using an array of 13 broadband, passive PZT sensors. \textbf{(b)} The array of PZT sensors are shown where the colors indicate their epicentral location with respect to the source and is used throughout the study. \textbf{(c)} Driver circuit for pulse source diagram showing the elements associated with the Elsys high-voltage pulsing unit (AE-HV-MUX). \textbf{(d)} The solution for the time-dependent pulse and discharge of the voltage applied across the PZT element using circuit theory. }
	\label{fig1} 
\end{figure}

@@

In Figure \ref{fig2b}(a) we look in detail at the position where the PZT actuator contacts steel plate. The actuator has threads on its body and is loaded on the plate by applying a small torque where the conical PZT tip is loaded through a thin layer of nickel (0.03 mm thick). This nickel foil is the cathode of the electro-mechanical circuit shown in Figure \ref{fig2b}(b), which represent a more detailed representation of the PZT actuator mentioned in the driver circuit (see Figure \ref{fig1}(c)). A small amount of contact gel is used to improve contact between the nickel cathode and steel plate but nickel was chosen due to is malleability and it formed a strong contact with the steel platen under minimal pressure \citep{Glaser1998}. To better understand the transient point force $f_{j}$ applied, we consulted literature in the biomedical industry that has studied piezomaterial, with similar pulsed excitation voltages, to perform ultrasonic reconstruction in acoustic media.  \citet{Christensen1988} looked at the pressure caused by a an electrical circuit that generated a sharp voltage pulse similar to that shown in Figure \ref{fig1}(d). Since the propagate waves through an acoustic medium they are interested in the time-dependent pressure boundary condition $p_{j}(\tau)$. To convert from pressure (over the tip area of the conical PZT) to an equivalent force $f_{j}$ we assume that the transient pressure field produced was uniform and therefore integrate over the contact tip area $A_{contact} = \pi r_{contact}^{2}$. For this PZT sensor the conical crystal has a contact radius of $r_{contact} = $ 0.75 mm. \cite{Christensen1988} found that the transient response of the pressure did not precisely duplicate the waveform of the voltage (see Figure \ref{fig1}(b)) due to the resonant properties of the crystal. When excited by a impulsive source, the crystal will resonate sinusoidal at its fundamental frequency and the wave will decay based in internal, external and transmitted losses.  The PZT actuator, when excited by the impulse, will produce a normalized pressure (or force-time function) described by the under-damped spring-mass damper system shown in Figure \ref{fig2b](c). \citet{Breckenridge1990} also showed evidence of under-damped behavior when exciting a conical PZT on an aluminium plate.

@@

%The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies. To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources. We also see potential benefits when studying changes acoustic transmissivity \citep{PyrakNolte1980} with more accurate and coupled models that the simple linear slip model \citep[LSM,][]{Kendall1957}.  By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty. We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.

\section{Conclusions}
We have followed the recently popularized methodology for sensor calibration coupled reasonable understanding of the wave propagation problem in a semi-infinite, homogeneous elastic half space. By fully characterizing the individual components of our system, we show that it is possible to better understand the force-produced by a conical PZT actuator when excited by a rapid high-voltage transient. While the results presented here are unique to our system, the methodology and insight into the characteristic shape of the force-time function can be easily reproduced in other acoustic emission system. Fully understanding how system responses change during an experiment is critical to properly interpret seismicity in a quantitative manner. Our approach for time-dependent updates to calibration parameters but also can provide intrinsic and quantitative understanding of changes in the transfer media.  
\section*{Acknowledgement}
T. M\"orgeli

@@

\subsection{Material Properties of PZT-5A (Navy II)}

\begin{table}[ht]
	\centering
	\caption{Material properties of Piezoelectric active source (PZT-5A).}
	\begin{tabular}{ m{5cm} m{2cm} m{4cm}} 
		\hline  
		\bf{Parameter} 		      & \bf{Symbol} 	  & \bf{Value}	\\
	   & \textit{Mechanical properties} & \\
	    Density                   & $\rho$            & 7500 kg/m$^{3}$\\
	    Poisson's ratio           & $\nu$             & 0.31\\
	    Young's modulus           & $E$               & 66 GPa\\
        Curie Point               & $T_{c}$           & 350 $^{o}$C\\  
        Mechanical quality factor &   $Q_{m}$         & 100\\
	  & \textit{Piezoelectric constants} & \\
 	  & d_{33}                   & 3.74 $\times$ 10$^{-10}$ m/V\\
 	  & d_{31}                   & -1.71 $\times$ 10$^{-10}$ m/V\\
	  & \textit{Dielectric constants} & \\
 	  & d_{33}                   & 3.74 $\times$ 10$^{-10}$ m/V\\
 	  & d_{31}                   & -1.71 $\times$ 10$^{-10}$ m/V\\

@@

\clearpage
\subsection{S2 Quality Factor}
We estimate the quality factor in steel $Q_{steel}$ from estimates of the force magnitude $A_{0}$ at different hypocentral distances. This follow typical theory on attenuation used to model the damping of seismic waves over distance due to internal intrinsic losses (e.g. friciton) in the material that decreased the energy per cycle\citep[e.g.][]{Barton2007}. From Figure \ref{fig9}(b) we have fit the exponential decay over distance with $A^{*}$ = 4.7 N and $\alpha$ = 0.01 m$^{-1}$. The quality factor depends on the frequencies of the propagating wave and can be expressed as a function as follows

>>>>

\begin{abstract}
We preform active source tests using a piezoelectric (PZT) actuator that was excited by a rapid transient high voltage pulse (HVP). The crystal geometry of the actuator was a conical frustum where the tip was placed centrally on top of a thick steel plate. We studied the elastodynamic stress waves  (between 100 kHz to 1 MHz) produced by the source, whereby the HVP pulse was converted to a rapid transient force-time function ($f_{j}$) via the piezoelectric effect.  The source produced mechanical vibrations ($u_{k}$) throughout the sample and was measured ($s$) using an array of 13 passive conical PZT receivers, at known locations on the bottom of the steel plate. Dynamic Green's functions ($G_{kj}$) were calculated using generalized ray theory and the known instrument responses ($I_{k}$) were pre-calculated from a series of ball drop experiments for all source-receiver pairs. Using these parameters, we were able to reconstruct the force-time function of the PZT actuator. As predicted from the literature, the actuator behaved as an under-damped oscillator with a peak loads, decay rate and undamped resonant frequency of $A_{0}$ = 4.7 $\pm$ 0.8 N, $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, respectively.  Both the decay rate and resonant frequency were determined as by minimizing the error between theoretical displacements for this force-time function over all 13 receiver measurements. Understanding calibrated force-time functions from PZT actuators can help to develop time-dependent and nondestructive characterization of many acoustic emission system components, such as the receiving transducers or the transfer media itself, in non-accessible laboratory environments. 
\end{abstract}

@@

Understanding the theory associated with elastodynamic wave propagation in materials has proven to be highly applicable to many disciplines in science and engineering. The general principle follows that by measuring the kinematic motion at a point in/on the media as its perturbed by the incoming elastic waves, we can use wave propagation theory to back calculate critical information of the problem. The particle motions within the body are governed by the wave equation and the body itself can be a solid or fluid materials. The waves carry both information of the media in which they propagate and of the source which caused them. This concept has made for many practical and highly interdisciplinary applications. It has been widely applied in the fields of seismology, biomedicine, and nondestructive testing, to name a few.

The concept relies heavily on understanding attributes to three key components: (\textit{i}) source, (\textit{ii}) material and (\textit{iii}) receiver as shown in Figure \ref{fig2}. In most applications, these waves are non-intrusive, propagating elastically through the medium from the source to receiver. From this, the problem benefits from \textit{source-receiver reciprocity} and due to symmetry of the wave equation, \textit{time invariance} applies, making this a versatile and flexible problem.

Sources can occur due to anthropogenic forcing, for example, rock samples subjected to outside stresses in a laboratory setting can crack locally, generating acoustic emissions \citep[e.g.][]{Lei2014, Moradian2016}. These emission cause vibrations within sample and these are recorded using peizoelectric sensors at known locations. This phenomena also scales up to mining activities where microseismic studies are performed to ensure safety during engineering activities \citep[e.g.][]{Manthei2018}. Further up the scale, large natural earthquakes on faults are activated by slow tectonic loading on geologic timescale. At each scale, the physic governing wave propagation holds and the vibrations through the medium are studied with arrays of sensors that are sensitive to vibrations at a range of frequencies. When the sources occur due to spontaneous instability, we consider this to be passive monitoring.

Sources can also be actively imposed, meaning that a transient force must manufactured within or on the body of interest. Since the wave equation still governs the motions throughout the body, it becomes an important tool to study the material properties or changes in them over time. Moreover, if multiple sources can be manufactured at varied locations, it becomes possible to understand structures through, for example, tomographic inversion.  This has been particularly important in the medical industry, where ultrasonic sensors can act as source or receivers and structures within the subject can be non-invasively reconstructed through ultrasound computer tomography (USCT) \citep[e.g.][]{Christensen1988}. While medical applications assume that acoustic waves propagate (i.e. fluid), \textit{active field surveys} in geophysics assume that the material is a solid and can reconstruct the subsurface to a high degree of certainty using `shot gather' approach and having well-constrained and repeatable sources.

@@

The study of waves in an elastic half-space was solved by \citet{Lamb1904} who was interested in the kinematic motions on a surface using the integral of plane waves solutions from \citet{Rayleigh1885}. More specifically, the Lamb's problem focuses on determining the elastic disturbance resulting from a point force in/on a half space. These early studies aimed to understand wave phase arrivals and their relationship to earthquake sources in the field of seismology. These seminal investigations have been followed by many hundreds of studies that have use different mathematical approaches to solve the wave equation \citep[e.g. ch 6 in][]{Aki2002}. These studies vary in complexity, for example in the media (in-homogeneous layered, or anisotropic, etc.), with the sources (double couple, compensated-linear-vector-dipole, etc.) and use a range of different methods to solve (theoretical closed-form solutions, numerical methods, etc.). We adopt the approach presented by \citet{Johnson1974} that derived the complete solution to the three-dimensional Lamb’s problem derived using the Cagniard--de Hoop method. This solution is used to study the mechanical disturbances from sources in an elastic half-space and has been implemented in a numerical generalized ray theory code by \citet{Hsu1985} \citep[see also][]{McLaskey2011, McLaskey2012, Selvadurai2019}.

While more complex sources have been considered to model earthquakes, such as the single and double couple source, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a). In Figure \ref{fig2}(a), we show the cross-section of the problem at hand. The source is produced by pulsing the piezoelectric actuator on the top surface using the experimental facilities described in Section \ref{ExpFac}. The impulsive actuation of the PZT crystal on the steel plate produces a rapid transient source causing elastodynamic stress waves to propagate outwards. In Figure \ref{fig2}, the coloured region represents a synthetic representation of the velocity wave-field and is only provided as a reference and is not representative of the wave-field we study here. This snapshot of the velocity wave-field represents that produced from a capillary fracture and was solved using a numerical finite element approach in ABAQUS \citep[adapted from fig. 2][]{Selvadurai2019}.

Properties of the source creating the stress waves is important. \citet{Breckenridge1990} states that the ideal source is infinitesimal in size, has a force-time function of a step or delta function, and generates large amplitudes. He performed important study of a variety of sources including pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive. He noted that each type is imperfect and has its trade offs. In this study, we look to aim to understand the PZT actuator (similar their conical transducer) which we can be leverage to non-invasively study the \textit{in situ} conditions inside less accessible experimental facility (e.g. triaxial pressure cell). To model the force-time function produced conical sensor, we first simplify the sequence of events and their components that link the source to the recorded signal.

In Figure \ref{fig2}, we show the five components of ``toolchain'' that is used to link the source to the measured signal and governed by the wave equation. The PZT actuator is used to produce (\textit{1}) a \textbf{rapid transient force} $f_{j}$ on the top surface at a point $\mathbf{\xi}$ of the steel platen at a delayed time $\tau$. Elastic stress waves propagate through the plate and the theoretical elastic displacement field throughout the body can be solved for using (\textit{2}) \textbf{Green's function} $G_{kj}$. The Green's functions map the (\textit{3}) \textbf{mechanical vibrations} $u_{k}$ at point $\mathbf{x}$ and time $t$ to the force at point $\mathbf{\xi}$ and time $\tau$. A passive sensor on the bottom surface at point $\mathbf{x}$ attempts to measure the theoretical displacements $u_{k}$. Unfortunately, all passive sensors distort the (\textit{4}) \textbf{measured signal}  $s$.  This distortion can be quantified according to its (\textit{5}) \textbf{instrument response} $i_{k}$.

\begin{figure}[h]
     	\centering
\includegraphics[scale= 1.0]{FIG2.pdf} 
\caption{Fundamental features related to the Lamb problem that relates elastodynamic displacements in an elastic half-space to a source (force-time) function. The velocity field is shown for reference only and was adopted from \citet{Selvadurai2019}. P and S waves are highlighted for reference only. The PZT actuator is located centrally on the top of the steel plate and passive (recording) sensors are shown below for the Section A-A from Figure \ref{fig1}(b).}
	\label{fig2} 
\end{figure}
\section{Experimental facilities}
\label{ExpFac}
\subsection{General}

We study elastodynamic waves propagating through an elastic isotropic, homogeneous steel plate. Using an electro-mechanical piezoelectric actuator, we deliver an impulsive transient source to the top surface of the steel specimen. An array of 13 piezoelectric (lead zirconate titanate, PZT) transducers are mounted on the  in an aluminium array holder. The aim of this study is to better understand the force produced by the piezoelectric actuator by studying the waves produced at different locations on the bottom of the specimen.

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1.0]{FIG1.pdf} 
\caption{\textbf{(a)} General schematic of the sensor calibration station at the Rock Physics and Mechanics Laboratory at ETH Zurich. We use this apparatus to apply an active source downwards using a PZT actuator located centrally on the top of a steel plate. This produced elastodynamic stress waves that are measured using an array of 13 broadband, passive PZT sensors on the bottom of the plate. \textbf{(b)} The array of passive PZT sensors are shown where the colors indicate their epicentral location with respect to the source and these colors used throughout the study. \textbf{(c)} The driver circuit for voltage pulse that shows the elements associated with the Elsys high-voltage pulsing unit (AE-HV-MUX). \textbf{(d)} The solution for the time-dependent voltage pulse and discharge applied across the PZT element. }
	\label{fig1} 
\end{figure}

@@

In Figure \ref{fig2b}(a) we look in detail at the position where the PZT actuator contacts steel plate. The actuator has threads on its body and is loaded on the plate by applying a small torque where the conical PZT tip is loaded through a thin layer of nickel (0.03 mm thick). This nickel foil is the cathode of the electro-mechanical circuit shown in Figure \ref{fig2b}(b), which represent a more detailed representation of the PZT actuator mentioned in the driver circuit (see Figure \ref{fig1}(c)). A small amount of contact gel is used to improve contact between the nickel cathode and steel plate but nickel was chosen due to is malleability and it formed a strong contact with the steel platen under minimal pressure \citep{Glaser1998}. To better understand the transient point force $f_{j}$ applied, we consulted literature in the biomedical industry that has studied piezomaterial, with similar pulsed excitation voltages, to perform ultrasonic reconstruction in acoustic media.  \citet{Christensen1988} looked at the pressure caused by a an electrical circuit that generated a sharp voltage pulse similar to that shown in Figure \ref{fig1}(d). Since the propagate waves through an acoustic medium they are interested in the time-dependent pressure boundary condition $p_{j}(\tau)$. To convert from pressure (over the tip area of the conical PZT) to an equivalent force $f_{j}$ we assume that the transient pressure field produced was uniform and therefore integrate over the contact tip area $A_{contact} = \pi r_{contact}^{2}$. For this PZT sensor the conical crystal has a contact radius of $r_{contact} = $ 0.75 mm. \cite{Christensen1988} found that the transient response of the pressure did not precisely duplicate the waveform of the voltage (see Figure \ref{fig1}(b)) due to the resonant properties of the crystal. When excited by a impulsive source, the crystal will resonate sinusoidal at its fundamental frequency and the wave will decay based in internal, external and transmitted losses.  The PZT actuator, when excited by the impulse, will produce a normalized pressure (or force-time function) described by the under-damped spring-mass damper system shown in Figure \ref{fig2b}(c). \citet{Breckenridge1990} also showed evidence of under-damped behavior when exciting a conical PZT on an aluminium plate.

@@

Will complete later.  The discussion in this type of study is not that important I believe.

\textcolor{red}{The hope is to adopt techniques that have widely been used in the field of exploration geophysics in novel laboratories acoustic emission studies. To our knowledge, the benefits seen at scale from applications such as \textit{controlled-source interferometry} have not been fully explored in the laboratory with fully calibrated PZT actuator sources. We also see potential benefits when studying changes acoustic transmissivity \citep{PyrakNolte1980} with more accurate and coupled models that the simple linear slip model \citep[LSM,][]{Kendall1957}.  By understanding how various waves will be produced by our sensor (P and S waves) we can potentially understand the spatial variability in $V_{P}/V_{S}$ ratios to a higher degree of certainty. We foresee that an accurate transient force-time functions of our PZT actuators will help to frequently and non-invasively update time-dependent characteristics of the acoustic emission system component, such as: changes in passive transducer responses, in the transfer media or more accurate characteristics of similarly doublet events.}

\section{Conclusions}
We have followed the recently popularized methodology for sensor calibration coupled reasonable understanding of the wave propagation problem in a semi-infinite, homogeneous elastic half space. By fully characterizing the individual components of our system, we show that it is possible to better understand the force-produced by a conical PZT actuator when excited by a rapid high-voltage transient. While the results presented here are unique to our system, the methodology and insight into the characteristic shape of the force-time function can be easily reproduced in other acoustic emission system. Fully understanding how system responses change during an experiment is critical to properly interpret seismicity in a quantitative manner. Our approach for time-dependent updates to calibration parameters but also can provide intrinsic and quantitative understanding of changes in the transfer media.

\section*{Acknowledgement}
The authors are indebted to the work and enthusiasm of Mr. T. M\"orgeli. He has been instrumental in the development of the infrastructure and provided critical input, design strategy and workmanship for the PZT actuator and the calibration station. His work is supported through the Rock Physics and Mechanics Laboratory at ETH Zurich.

Mr. Wu has been supported financially by China Scholarship Council (CSC, No. 201806440037).

Dr. Selvadurai has was funded under FILL IN ASK STEFAN.

Dr. Madonna was funded ...

Dr. Moradian was funded ...

@@

\*subsection{Material Properties of PZT-5A (Navy II) }
\begin{table}[ht]
	\centering
	\caption{Material properties of Piezoelectric active source (PZT-5A).}
	\begin{tabular}{ m{5cm} m{2cm} m{4cm}} 
		\hline  
		\bf{Parameter} 		      & \bf{Symbol} 	  & \bf{Value}	\\
	   & \textit{Mechanical properties} & \\
	    Density                   & $\rho$            & 7500 kg/m$^{3}$\\
	    Poisson's ratio           & $\nu$             & 0.31\\
	    Young's modulus           & $E$               & 66 GPa\\
        Curie Point               & $T_{c}$           & 350 $^{o}$C\\  
        Mechanical quality factor &   $Q_{m}$         & 100\\
	  & \textit{Piezoelectric constants} & \\
 	  & d_{33}                   & 3.74 $\times$ 10$^{-10}$ m/V\\
 	  & d_{31}                   & -1.71 $\times$ 10$^{-10}$ m/V\\
	  & \textit{Dielectric constants} & \\
 	  & d_{33}                   & 3.74 $\times$ 10$^{-10}$ m/V\\
 	  & d_{31}                   & -1.71 $\times$ 10$^{-10}$ m/V\\

@@

\clearpage
\subsection*{S2 Quality Factor}
We estimate the quality factor in steel $Q_{steel}$ from estimates of the force magnitude $A_{0}$ at different hypocentral distances. This follow typical theory on attenuation used to model the damping of seismic waves over distance due to internal intrinsic losses (e.g. friciton) in the material that decreased the energy per cycle\citep[e.g.][]{Barton2007}. From Figure \ref{fig9}(b) we have fit the exponential decay over distance with $A^{*}$ = 4.7 N and $\alpha$ = 0.01 m$^{-1}$. The quality factor depends on the frequencies of the propagating wave and can be expressed as a function as follows
